\documentclass{muratcan_cv}

\setname{Dr. Matías Javier}{Micheletto}
\setaddress{Bahía Blanca - Argentina}
\setmobile{+54 9 291 4380079}
\setmail{matiasmicheletto@gmail.com}
\setposition{Work Student} 
\setlinkedinaccount{https://www.linkedin.com/in/matiasmicheletto/}
\setgithubaccount{https://matiasmicheletto.github.io}
\setthemecolor{red}

\begin{document}
\headerview
\vspace{1ex}

\addblocktext{Summary}{
After obtaining my Electronic Engineering degree, I started working as PhD candidate under a CONICET intern scholarship where acquired skills and experience in data science, software and hardware development applied to a wide variety of applications and collaborating with researchers from different disciplines. I have worked as teaching assistant and have published 5+ articles in international journals and participated in 15+ national and international conferences related to technology, education and engineering.
}

\section{Education} 
    \datedexperience{Universidad Nacional del Sur}{2016-2021} 
    \explanation{PhD Engineering} 
    \explanationdetail{\coloredbullet\
     Thesis title: ``Development of Computer Systems for Supporting Agricultural Work in the Southwest of the Buenos Aires Province''. Thesis grade: 10/10.
     }
    \explanationdetail{\coloredbullet\
     Advisors: Dr. Rodrigo M. Santos and Dr. Juan A. Galantini.
     }
    \datedexperience{Universidad Nacional del Sur}{2007-2016} 
    \explanation{B.S. Electronic Engineering} 
     \explanationdetail{\coloredbullet \ 
     GPA: 8.17/10. Awarded with four undergraduate student scholarships and a one-year internship.
     }
    

\section{Experience}
    %
    \datedexperience{CAPP Mobile BB S.R.L.}{2019} 
    \explanation{Front-end software developer} 
    \explanationdetail{\coloredbullet\
     Collaboration in the design and implementation of the CAPP mobile application, backoffice, admin panel and shop website.
     }
    %
    \datedexperience{Neufitech S.R.L.}{2017-2019} 
    \explanation{Full-stack web developer and IoT Engineer} 
    \explanationdetail{\coloredbullet\
     Design and implementation of a PWA platform. Desing and implementation of IoT devices as interfaces for disabled people.
     }
    %
    \datedexperience{Universidad Nacional del Sur}{2016-2020} 
    \explanation{Teaching assistant} 
    \explanationdetail{\coloredbullet\
     Digital electronic courses for engineering students.
     }
    
    
\section{Skills}
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  HTML+JS+CSS \cpshalf C++ \cpshalf Matlab \ \ \textbf{\emph{Familiar:}} \ \  Python \cpshalf SQL \cpshalf Java}}
    \newcommand{\skillthree}{\createskill{Data Science Tools \ \& \ Libraries}{Jupyter \cpshalf Matplotplib \cpshalf Numpy \cpshalf Pandas \cpshalf Scikit-learn}}
    \newcommand{\skillfour}{\createskill{Web Frameworks and Tools}{ReactJS \cpshalf Angular 1 \cpshalf Bootstrap \cpshalf Materialize \cpshalf Framework7 \cpshalf Firebase \cpshalf Heroku}}
    \newcommand{\skillfive}{\createskill{Mobile Development}{ Apache Cordova \cpshalf React Native }}
    \newcommand{\skillsix}{\createskill{IoT and Embedded Systems}{ Arduino \cpshalf NodeMCU \cpshalf Raspberry }}
    \createskills{\skillone, \skillthree, \skillfour, \skillfive, \skillsix}
    
\section{Extra}
    \newcommand{\extraone}{
    Awarded 2nd place ``Agroton 2018'' (24hr innovation contest).
    }
    \newcommand{\extratwo}{
    Teaching and coaching habilities acquired through 5+ years experience in college's engineering courses.
    }
    \newcommand{\extrathree}{
    Creative problem solver, detailed and meticulous.
    }
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    \createbullets{\listofextras}

\createfootnote
\end{document}
